APIs for hyperparameter optimization in scikit-learn

### 2013-05-13 paper.tex
cleanup and ruthless propaganda

The main goal of the scikit-learn project
is to provide high-quality implementations
of ``classic'' machine learning algorithms
with a consistent API.
This paper explores the role that such an API plays
for handling the problem of hyperparameter optimization,
also known as \textit{model selection} (\citealp{elemstatlearn}:219--257).

>>>>

The main goal of the scikit-learn project
is to provide high-quality implementations
of ``classic'' machine learning algorithms
with a consistent and clear API.
This paper explores the role that such an API plays
for handling the problem of hyperparameter optimization,
also known as \textit{model selection} (\citealp{elemstatlearn}:219--257).
